## Homework 3

<!--
You can use the example3.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework3.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->
The first step is to read in the data
```{r}
dat<-read.csv("homework3.csv")
```



<!--
Check the structure of the data.
-->
The next step is to check the structure
```{r}
str(dat)
```
As we can see dat is a data frame with 3 variables: major, year in college, and the level of conservatism.
<!--
Find the mean, median, and standard deviation using the sd() function
for the overall level of conservatism.
-->

Now we will find the mean, median and variance of the overall level of conservatism.
```{r}
mean(dat$conservatism)
```
```{r}
median(dat$conservatism)
```
```{r}
sd(dat$conservatism)
```

From the previous analyses we can see that the mean level of conservatism is 52.3, the median is 53.8, and the standard deviation is 19.8 

<!--
Find the mean level of support for freshmen only.
-->
Now we will see what the mean level of support is for freshman. 
```{r}
mean(dat$conservatism[dat$year=="freshman"])
```
Here we can see that the mean for freshman is 47.5

<!--
Find the mean level of support for male business students only.
-->
Now we will find the mean level of support for sophomore business students.
```{r}
mean(dat$conservatism[dat$year=="sophomore" & dat$major=="business"])
```
Here we can see that the mean is 61.6
