---
title: "CapstoneProject"
author: "Ashley Maxwell"
date: "May 11, 2016"
output: html_document
---

```{r}
dat<-read.csv("Questiondata.csv")
```

```{r}
str(dat)
```
As we can see dat from the data frame has four variables:Cover, Home, Coffee, Article
```{r}
dat$total = dat$Cover + dat$Home + dat$Coffee
```

```{r}
mean(dat$Cover[dat$Article=="positive"])
mean(dat$Home[dat$Article=="positive"])
mean(dat$Coffee[dat$Article=="positive"])
```

```{r}
mean(dat$Cover[dat$Article=="neutral"])
mean(dat$Home[dat$Article=="neutral"])
mean(dat$Coffee[dat$Article=="neutral"])
```

It looks like the means for the positive articles are slightly smaller than the means for neutral articles, which would show that people were manipulated by the article. I will run an independent t-test to test if the neutral group's mean differed significantly from the mean of the positive group.  

```{r}
t.test(dat$Cover[dat$Article=="positive"],
       dat$Cover[dat$Article=="neutral"],
       var.equal=TRUE,)
```
The t-test reveals that there is not a significant difference between the positive and neutral article responses for cover, t(71)= -.225, p= ,85

```{r}
t.test(dat$Home[dat$Article=="positive"],
       dat$Home[dat$Article=="neutral"],
       var.equal=TRUE,)
```
The t-test shows that there is no significant difference between the positive and neutral article responses for Home, t(71)= -.245, p=.81
```{r}
t.test(dat$Coffee[dat$Article=="positive"],
       dat$Coffee[dat$Article=="neutral"],
       var.equal=TRUE,)
```
The t-test shows that there is no significant difference between the positive and neutral article responses for Coffee, t(71)= -.138, p= .89

To test the alternative hypothesis that the positive responses differed significantly from the neutral, I will run another t-test.
```{r}
t.test(dat$Coffee[dat$Article=="positive"],
       dat$Coffee[dat$Article=="neutral"],
       var.equal=TRUE,
       alternative="greater")
```

```{r}
t.test(dat$Home[dat$Article=="positive"],
       dat$Home[dat$Article=="neutral"],
       var.equal=TRUE,
       alternative="greater")
```

```{r}
t.test(dat$Cover[dat$Article=="positive"],
       dat$Cover[dat$Article=="neutral"],
       var.equal=TRUE,
       alternative="greater")
```
From the results of the t-tests that tests the alternative hypothesis, we can see that there is no significNant difference between the two groups positive and neutral. 
